Incentivizing Exploration by Heterogeneous Users

### 2018-05-14 abstract.tex
fixed a few typos

We propose an algorithm that incentivizes arms played infrequently in the
past whose probability of being played in the next round would be small
without incentives.
Under the assumption that each arm is preferred by at
least a fraction $\MinProb > 0$ of agents,
we show that this algorithm achieves expected
cumulative regret of $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
If \MinProb is known or the distribution over agent
preferences is discrete,
the exponential term $\e^{2/\MinProb}$ can be replaced with suitable
polynomials in \ARMNUM and $1/\MinProb$.
For discrete preferences, the regret dependence on $T$ can be
eliminated entirely, giving constant (depending only polynomially on
\ARMNUM and $1/\MinProb$) expected regret and payments.
This constant regret stands in contrast to the $\Theta(\log(T))$ dependence of
regret in standard multi-armed bandit problems.
It arises because even unobserved heterogeneity in agent preferences
allows exploitation of arms to also explore arms fully;
succinctly, heterogeneity provides free exploration.

>>>>

We propose an algorithm that incentivizes arms played infrequently in the
past whose probability of being played in the next round would be small
without incentives.
Under the assumption that each arm is preferred by at
least a fraction $\MinProb > 0$ of agents,
we show that this algorithm achieves expected
cumulative regret of $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$, where $\ARMNUM$ is the total number of arms.
If \MinProb is known or the distribution over agent
preferences is discrete,
the exponential term $\e^{2/\MinProb}$ can be replaced with suitable
polynomials in \ARMNUM and $1/\MinProb$.
For discrete preferences, the regret dependence on $T$ can be
eliminated entirely, giving constant (depending only polynomially on
\ARMNUM and $1/\MinProb$) expected regret and payments.
This constant regret stands in contrast to the $\Theta(\log(T))$ dependence of
regret in standard multi-armed bandit problems.
It arises because even unobserved heterogeneity in agent preferences
allows exploitation of arms to also explore arms fully;
succinctly, heterogeneity provides free exploration.

### 2018-05-14 colt.tex
moved some proofs to the appendix
re-state lemmas/proofs in the appendix
Broke algorithm.tex up into 4 files.
copied changes from 4.4 to appendix, rearranged appendix order
fixed a few typos

@@

@@

\title{Incentivizing Exploration by Heterogeneous Users}
% {Incentivizing Exploration with Heterogeneous Utilities}

%\author{\name Bangrui Chen \email bc496@cornell.edu \\
%\name Peter I.\ Frazier \email pf98@cornell.edu \\
%\addr Operations Research and Information Engineering\\
%Cornell University\\
%New York, NY 14850, USA
%\AND
%\name David Kempe \email david.m.kempe@gmail.com  \\
%\addr Department of Computer Science\\
%University of Southern California\\
%Los Angeles, CA 90089, USA}

@@

\begin{keywords}
Incentivizing Exploration, Multi-Armed Bandits
\end{keywords}

@@

\input{algorithm}

@@

@@

>>>>

\newcommand{\emptyextraproof}[1]{\rm \trivlist \item[\hskip \labelsep{\bf Proof of #1. }]}
\def\endemptyextraproof{\endtrivlist}

@@

\newenvironment{rlemma}[3][]{

@@

\title{Incentivizing Exploration by Heterogeneous Users}

\author{\name Bangrui Chen \email bc496@cornell.edu \\
\name Peter I.\ Frazier \email pf98@cornell.edu \\
\addr Operations Research and Information Engineering\\
Cornell University\\
New York, NY 14850, USA
\AND
\name David Kempe \email david.m.kempe@gmail.com  \\
\addr Department of Computer Science\\
University of Southern California\\
Los Angeles, CA 90089, USA}

@@

\begin{keywords}
Incentivizing Exploration, Multi-Armed Bandits, Social Learning
\end{keywords}

@@

\input{algorithm_intro}
\input{algorithm_general}
\input{algorithm_payment}
\input{algorithm_regret}

@@

\input{Lemmas}

@@

\input{Discussion-Proof}

### 2018-05-14 introduction.tex
fixed a few typos

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction \MinProb
of the population likes this arm best,
and let \TieDensity be a measure of the ``density of near-ties''
between agents' arm preferences
(in a sense made precise in Section~\ref{subsec:discrete}).
There is a policy that achieves expected 
cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
In particular, when $\TieDensity = 0$
(e.g., in the case of discrete agent preferences),
both the expected regret and expected payment are bounded by constants
(with respect to $T$). 
\end{theorem}

>>>>

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction \MinProb
of the population likes this arm best,
and let \TieDensity be a measure of the ``density of near-ties''
between agents' arm preferences
(in a sense made precise in Section~\ref{subsec:discrete}).
There is a policy that achieves expected 
cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
In particular, when agents who are close to tied between two arms have measure $0$,
both the expected regret and expected payment are bounded by constants
(with respect to $T$). 
\end{theorem}

### 2018-05-14 problem_setting.tex
edits to algo intro, and problem statement
fixed a few typos

Since each user only pulls an arm once, users are \emph{myopic}:
in the absence of incentives, user $t$ will pull an arm from
$\argmax_i \AgentV{t} \cdot \ArmEV{t}{i}$.
To incentivize users to explore more, the principal can offer
\emph{payments} $\Pay{t}{i}$ to user $t$ for pulling arm $i$.
Then, user $t$ will pull an\footnote{We assume that ties are broken in
  favor of an arm with largest payment \Pay{t}{i}.}
% ; this assumption is
%   only for notational convenience, and can of course be avoided by
%   raising payments infinitesimally.
%   \pfcomment{In the finite preference setting this is clear, but it's a little bit delicate when there are continuum preferences, since regardless of the payment we offer there may always be support within our preference distribution for a $\theta$ that causes a tie.  In this continuum setting it should instead be possible to perturb infinitessimally so that we avoid ties with probability 1.}  
% }
arm $i$ maximizing $\argmax_i (\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
The principal cannot observe \AgentV{t},
and only knows the distribution \AgentDist from which it is drawn.
Her goal is to reduce both the cumulative
\emph{regret} experienced by all users up to time $T$,
and the total \emph{payment} she makes to the users.

@@

Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Set{\AgV}{\Best{\AgV} = i}}$
denote the minimum (over all arms) fraction of users that prefer any
particular arm.

@@

>>>>

Since each user only pulls an arm once, users are \emph{myopic}:
in the absence of incentives, user $t$ will pull an arm from
$\argmax_i \AgentV{t} \cdot \ArmEV{t}{i}$.
To incentivize users to explore more, the principal can offer
\emph{payments} $\Pay{t}{i}$ to user $t$ for pulling arm $i$.
Then, user $t$ will pull an\footnote{We assume that ties are broken in
  favor of an arm with largest payment \Pay{t}{i}.}
% ; this assumption is
%   only for notational convenience, and can of course be avoided by
%   raising payments infinitesimally.
%   \pfcomment{In the finite preference setting this is clear, but it's a little bit delicate when there are continuum preferences, since regardless of the payment we offer there may always be support within our preference distribution for a $\theta$ that causes a tie.  In this continuum setting it should instead be possible to perturb infinitessimally so that we avoid ties with probability 1.}  
% }
arm $i$ maximizing $(\Pay{t}{i} + \AgentV{t} \cdot \ArmEV{t}{i})$.
The principal cannot observe \AgentV{t},
and only knows the distribution \AgentDist from which it is drawn.
Her goal is to reduce both the cumulative
\emph{regret} experienced by all users up to time $T$,
and the total \emph{payment} she makes to the users.

@@

Let $\MinProb = \min_{i} \Prob[\AgentDist]{\Best{\AgV} = i}$
denote the minimum (over all arms) fraction of users that prefer any
particular arm.

@@

We emphasize that this assumption implies ties happen with probability $0$.

### 2018-05-14 result_discussion.tex
fixed a few typos

We compare these bounds to those for standard bandits,
focusing on the dependence on $T$.  
The standard bandit setting is the case when the agent types \AgV
are concentrated on a single point, and agents pull arms at the
principal's direction without requiring payment.
(Notice that this setting violates our Assumption~\ref{A3},
so out bounds do not apply to it.)
Then, the payment is $0$ and the expected regret scales as
$\Theta(\log(T))$ \cite[Theorem 2.1]{bubeck2012regret}.

>>>>

We compare these bounds to those for standard bandits,
focusing on the dependence on $T$.  
The standard bandit setting is the case when the agent types \AgV
are concentrated on a single point, and agents pull arms at the
principal's direction without requiring payment.
(Notice that this setting violates our Assumption~\ref{A3},
so our bounds do not apply to it.)
Then, the payment is $0$ and the expected regret scales as
$\Theta(\log(T))$ \cite[Theorem 2.1]{bubeck2012regret}.
